\documentclass[10pt]{article}

\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage[margin=1.3cm, top=2.3cm]{geometry}

\setlength{\parindent}{0pt}

\pagestyle{fancy}
\lhead{Helix}
\rhead{Page \thepage}
\cfoot{}

\title{\framebox[0.8\textwidth]{Supa Moba}}
\author{v0.2\\Boice Wong\\Isaiah Discipulo\\Jacob Ragsdale}
\date{August 2019}

\begin{document}
	\clearpage\maketitle
	\thispagestyle{empty}
	\pagebreak
	
	\tableofcontents
	\pagebreak
	
	\section{Introduction}
		\subsection{Rights}
			This document specifies a design for a game with the provisional title "Supa Moba". The ideas and concepts presented in this document are the intellectual property of Boice Wong, Isaiah Discipulo, and Jacob Ragsdale.
			
		\subsection{Version Conventions}
			The version number for this document is written X.Y, with the X incrementing when the meaning of this document is altered, such as adding or removing a game feature; and the Y incrementing when the document is edited for grammar or clarity.
			
		\subsection{Concept}
			The aim of Supa Moba is to create an 8-bit style, multiplayer online battle arena game, combining the best aspects of the genre (League of Legends, DOTA, etc.) while providing innovations to improve upon genre drawbacks.
	
	\section{Overview}
		Players will fight in teams of three, attempting to capture the enemies' core. The cores will be connected by two lanes and a central "jungle". The two lanes will be guarded by towers that attack enemies and minions, which spawn periodically at each core and march down a lane. A core cannot take damage until all of the towers in at least one lane have been destroyed. The game ends when one team has destroyed the others' core. 
		
	\section{Pillars of Play}
		\subsection{Player vs. Enemy}
			As players kill enemy minions and towers they will gain a resource (with the placeholder name "foo") that can be spent to level up, increasing their power for the current game. Within the jungle, special minions will spawn regularly, either granting foo or some other resource on death.
			
		\subsection{Player vs. Player}
			Players can also gain foo by killing other players. Players who die will respawn at their base, with respawn time varying as the game continues.
		
		\subsection{Character Management}
			As characters accumulate foo they can spend it to increase their power in a variety of ways, allowing them to customize their playstyle.
		
	\section{Technology}
		The game will be built with Love2D, a sparse, lua game engine. This will provide rendering and audio functions; however, we will have to build all of the aforementioned functionality, including but not limited to:\\
		\begin{tabular} {ll}
			-&Collision resolution\\
			-&Game logic\\
			-&Additional graphic effects\\
			-&Game as a web socket client\\
			-&Game as a web socket server\\
		\end{tabular}
		
			
	\section{Timeline}
		\begin{tabular} {ll}
			Sprint 0& Begin working on engine structure\\
			Sprint 1& Be able to control 6 characters simultaneously in an online environment\\
			Sprint 2& Implement basic combat mechanics\\
			Sprint 3& Implement towers and minions\\
			Sprint 4& Implement character progression mechanics\\
			Sprint 5& Implement out-of-game features, e.g. character select, game lobbies\\
		\end{tabular}
		
\end{document}